Title

### 2013-04-02 inc/design_considerations/considerations.tex
merge Andreas' comments through child's law section

It is easy to believe that in order to make a useful image in an electron microcope, the number of electrons collected must be above some minimum number.
The Rose criterion \cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k $\times$ 1k CCD camera, this implies an incident electron pulse with $N=10^8$ \cite{armstrong_prospects_2007}.

@@

By definition, for single-shot imaging with a DTEM, all of the electrons used to form an image must be contained in a single pulse.
In a single-shot DTEM, destructive measurements will usually result in useful images, in fact, the dynamics being studied are often destructive, regardless of the knock-on damage cause by the probe.
However, although sample damage concerns may be neglected, the use of a pinhole is likely to reduce the pulse charge below the useful level.
This means that the designer of a DTEM must endeavor to retain and utilize all of the generated electrons.

@@

Since we are now aware that there is a large minimum number of electrons needed per pulse, it is only natural to ask if there is the practical limit on how much charge (i.e., the number of electrons/pulse, $N$) can be extracted from a pulsed laser-driven DC photoelectron gun.
When the incident laser pulse duration $\tau$ is longer than the time-of-flight (TOF) $t_{gun}$ of a single electron across the acceleration gap $d$ of the DC gun with a potential $V_{DC}$, $\tau > t_{gun} = d \sqrt{2m/eV_{DC}}$, then the maximum photocurrent density $J_{CL}$ is given by the well-known Child-Langmuir law \cite{child_discharge_1911,langmuir_effect_1923}:
\begin{equation}
  J_{CL} = \frac{4 \varepsilon_0}{9} \sqrt{\frac{2e}{m}} \frac{V_{DC}^{3/2}}{d^2}
\end{equation}
where $e$ is the electron charge and $\varepsilon_0$ is the vacuum permittivity.

@@

In this short pulse case, an equivalent diode approximation \cite{valfells_effects_2002} allows for the definition of a critical current density associated with virtual cathode formation in terms of the steady-state Child-Langmuir limit:
\begin{equation}
  J_{crit} = \frac{27}{4} \left ( \frac{ 1 - \sqrt{1-\tfrac{1}{3} \chi^2} }{ \chi^3 } \right ) J_{CL}
\end{equation}
where $\chi = \tau_e / t_{gun}$.
When $\chi \ll 1$, the usual case in UEM, the critical current density is simply given by
\begin{equation}
  J_{crit} = \frac{\varepsilon_0 E_{DC}}{\tau_e}
\end{equation}
where the DC gun field $E_{DC} = V_{DC}/d$.
This relation may be rewritten to yield a critical number of photoemitted electrons/pulse before virtual cathode formation:
\begin{equation} \label{eq:n_crit}
  N_{crit} = \frac{\pi \varepsilon_0 w^2 V_{DC}}{e d}
\end{equation}
In obtaining the above equation, we have used an irradiated photocathode area of $\pi w^2$ associated with an incident Gaussian laser pulse of the form of \ref{eq:laser_form}.
The relation clearly indicates that $N_{crit}$ is only dependent upon the initial DC surface field (i.e., $E_{DC}$) at the photocathode and the illuminated area --- as expected because a virtual cathode forms when the initial photocathode surface charge density associated with $E_{DC}$ is photoemitted, effectively screening the cathode from the acceleration field.

@@

This finally leads to the first consideration for UEM design mentioned in the introduction: for the clean pulsed emission of sufficient to create a useful image, the generated beam should have a HW1/eM width 
\begin{equation} \label{eq:minimum_w}
  w \gtrsim \sqrt{\frac{N e d}{\pi \varepsilon_0 V_{DC}}} \,\text{.}
\end{equation}
For our example case above, to cleanly extract $N \ge 10^8$ electrons/pulse we require $w \gtrsim 0.56 \text{ mm}$.
I will discuss the effect that accomodating a large pulse size has on designing an Ultrafast Electron Microscope in Chapter \ref{chap:prototype}.

>>>>

It is straightforward to show that in order to make a useful image in an electron microcope, the number of electrons collected must be above some minimum number.
The Rose criterion \cite{rose_television_1948} indicates that an average detector signal strength of $\sim$100 electrons/pixel is required for adequate gray scaling of the image.
For a 1k $\times$ 1k CCD camera, this implies an incident electron pulse with $N=10^8$ \cite{armstrong_prospects_2007}.

@@

By definition, for single-shot imaging with a DTEM, all of the electrons used to form an image must be contained in a single pulse.
In a single-shot DTEM, the dynamics being studied are often destructive, regardless of the knock-on damage cause by the probe pulse; what matters is that the system be able to probe the sample before it is destroyed.
Nevertheless, although sample damage concerns may be neglected, the use of a pinhole is likely to reduce the pulse charge below the useful level.
This means that the designer of a DTEM must endeavor to retain and utilize all of the generated electrons.

@@

Since we are now aware that there is a large minimum number of electrons needed per pulse, it is only natural to ask if there is the practical limit on how much charge (i.e., the number of electrons/pulse, $N$) can be extracted from a pulsed laser-driven DC photoelectron gun.
When the incident laser pulse duration $\tau$ is longer than the time-of-flight (TOF) $t_{gun}$ of a single electron across the acceleration gap $d$ of the DC gun with a potential $V_{DC}$, $\tau > t_{gun} = d \sqrt{2m/eV_{DC}} \approx 0.1-1$ns, typically, then the maximum photocurrent density $J_{CL}$ is given by the well-known Child-Langmuir law \cite{child_discharge_1911,langmuir_effect_1923}:
\begin{equation}
  J_{CL} = \frac{4 \varepsilon_0}{9} \sqrt{\frac{2e}{m}} \frac{V_{DC}^{3/2}}{d^2}
\end{equation}
where $e$ is the electron charge and $\varepsilon_0$ is the vacuum permittivity.

@@

In this short pulse case, an equivalent diode approximation \cite{valfells_effects_2002} allows for the definition of a critical current density associated with virtual cathode formation in terms of the steady-state Child-Langmuir limit:
\begin{equation}
  J_{crit} = \frac{27}{4} \left ( \frac{ 1 - \sqrt{1-\tfrac{1}{3} \chi^2} }{ \chi^3 } \right ) J_{CL}
\end{equation}
where $\chi = \tau_e / t_{gun}$.
When $\chi \ll 1$, the usual case in UEM, the critical current density is simply given by
\begin{equation}
  J_{crit} = \frac{\varepsilon_0 E_{DC}}{\tau_e}
\end{equation}
where the DC gun field $E_{DC} = V_{DC}/d$.
This relation may be rewritten to yield a critical number of photoemitted electrons/pulse before virtual cathode formation:
\begin{equation} \label{eq:n_crit}
  N_{crit} = \frac{\pi \varepsilon_0 w^2 V_{DC}}{e d}
\end{equation}
In obtaining the above equation, we have used an irradiated photocathode area of $\pi w^2$ associated with an incident Gaussian laser pulse of the form of \ref{eq:laser_form}.
The relation clearly indicates that $N_{crit}$ is only dependent upon the initial DC surface field (i.e., $E_{DC}$) at the photocathode and the illuminated area --- as expected, because a virtual cathode forms when the initial photocathode surface charge density associated with $E_{DC}$ is photoemitted, effectively screening the cathode from the acceleration field.

@@

This finally leads to the first consideration for UEM design mentioned in the introduction: for the clean pulsed emission of sufficient to create a useful image, the generated beam should have a HW1/eM width 
\begin{equation} \label{eq:minimum_w}
  w \gtrsim \sqrt{\frac{N e d}{\pi \varepsilon_0 V_{DC}}} \,\text{.}
\end{equation}
For our example case above, to cleanly extract $N \ge 10^8$ electrons/pulse we require $w \gtrsim 0.56 \text{ mm}$.
The effect that accomodating a large transverse pulse size has on designing an Ultrafast Electron Microscope will be discussed in Chapter \ref{chap:prototype}.
